Artin Group Presentations Arising from Cluster Algebras

### 2014-08-03 Presentation/Prob6.tex
Revert "Updated beamer"
This reverts commit d38ecf4a1ba4eb9efaaa745f829e64a12a978cd2.

\usepackage[english]{babel}
%\usepackage[utf8x]{inputenc}
\usepackage{mathrsfs}

\newtheorem{proposition}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{question}{REU Problem}

@@

\begin{frame}{Mutation Rules}
\begin{proposition}
\cite[Proposition 1.4]{BM}
Let $B$ be a $2$-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows:
\begin{itemize}
\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
\item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e. with $a,b$ positive), let $c$ be the weight on the edge $j \rightarrow i$, taken to be zero if there is no such arrow. Let $c'$ be determined by $c'\geq 0$ and 
$c+c' =$ max$(a,b)$. 
Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.

@@

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{proposition}
\cite[Proposition 2.1]{BM}
Any chordless cycle in $\Gamma$ must have an unoriented structure that is one of the following. Furthermore, it must be cyclically oriented.
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{chordlesscycles.PNG}
\caption{Possible chordless cycles in a diagram}
\end{figure}

@@

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{lemma}
\cite[Lemma 2.2]{BM}
For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{3vertconnected.PNG}
\caption{Unoriented 3-vertex connected subdiagrams}
\end{figure}
\end{lemma}

@@

\begin{frame}{Possible mutations for $i\--\ k\--\ j$}
\begin{corollary}
\cite[Corollary2.3]{BM}
If in $\Gamma$ we have $i,j,k \in V(\Gamma), i \neq k \neq j$, and we have $i\--\ k\--\ j$, then the only possible mutations for this connected path between the three vertices are the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .40]{mutation3path.PNG}
\caption{Mutation of three connected vertices}
\end{figure}
\end{corollary}
\end{frame}

@@

\begin{theorem}
\cite[Theorem 5.4]{BM} 
\begin{enumerate}
\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
\item Let $\mathscr{A}$ be a cluster algebra of finite type. Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
\end{enumerate}
\end{theorem}
\end{frame}

@@

Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}}.$$
\end{block}

\end{frame}
\begin{frame}
Now we have 
\begin{align*}
\langle x_i,x_j \rangle ^k = \begin{cases}
(x_ix_j)^{\frac{k}{2}}, &\text{ if }k \equiv 0 \pmod 2\\
(x_ix_j)^{\frac{k-1}{2}}x_i &\text{ if } k \equiv 1 \pmod 2
\end{cases}
\end{align*}
And $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}}.$$

Additionally, let $$t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1})  s_{i_a}^{-1}p(i_a,i_{a+1})^{-1}.$$

@@

\begin{frame}
Given a diagram $\Gamma$ of finite type, we define the Artin group $A_{\Gamma}$ with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations (noting that $t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1})  s_{i_a}^{-1}p(i_a,i_{a+1})^{-1}$):

@@

\begin{frame}
\begin{thebibliography}{69}

\bibitem{BM}[1] Barot, M. and Marsh, R., Reflection Group Presentations Arising from Cluster Algebras, \emph{Preprint}, arXiv:1112.2300 (2011)

\end{thebibliography}

>>>>

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathrsfs}

\newtheorem{proposition}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{question}{Question}

@@

\begin{frame}{Mutation Rules}
\begin{proposition}
%%CITE BAROT MARSH PROP 1.4
%\alert{Proposition 1.4}
Let $B$ be a $2$-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows:
\begin{itemize}
\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
\item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e. with $a,b$ positive), let $c$ be the weight on the edge $j \rightarrow i$, taken to be zero if there is no such arrow. Let $c'$ be determined by $c'\geq 0$ and 
$c+c' =$ max$(a,b)$. 
Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.

@@

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{proposition}
%%CITE \alert{Proposition 2.1}
Any chordless cycle in $\Gamma$ must have an unoriented structure that is one of the following. Furthermore, it must be cyclically oriented.
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{chordlesscycles.PNG}
\caption{Possible chordless cycles in a diagram}
\end{figure}

@@

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{lemma}
%CITE \alert{Lemma 2.2}
For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{3vertconnected.PNG}
\caption{Unoriented 3-vertex connected subdiagrams}
\end{figure}
\end{lemma}

@@

\begin{frame}{Possible mutations for $i\--\ k\--\ j$}
\begin{corollary}
%CITE \alert{Corollary 2.3}
If in $\Gamma$ we have $i,j,k \in V(\Gamma), i \neq k \neq j$, and we have $i\--\ k\--\ j$, then the only possible mutations for this connected path between the three vertices are the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .40]{mutation3path.PNG}
\caption{Mutation of three connected vertices}
\end{figure}
\end{corollary}
\end{frame}

@@

\begin{theorem}
%CITE \alert{Theorem 5.4} 
\begin{enumerate}
\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
\item Let $\mathscr{A}$ be a cluster algebra of finite type. Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
\end{enumerate}
\end{theorem}
\end{frame}

@@

Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}} s_{i_{a}}^{-1}.$$
\end{block}

\end{frame}
\begin{frame}
Now we have 
\begin{align*}
\langle x_i,x_j \rangle ^k = \begin{cases}
(x_ix_j)^{\frac{k}{2}}, &\text{ if }k \equiv 0 \pmod 2\\
(x_ix_j)^{\frac{k-1}{2}}x_i &\text{ if } k \equiv 1 \pmod 2
\end{cases}
\end{align*}
And $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}} s_{i_{a}}^{-1}.$$

Additionally, let $$t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1}) p(i_a,i_{a+1})^{-1} s_{i_a}^{-1}.$$

@@

\begin{frame}
Given a diagram $\Gamma$ of finite type, we define the Artin group $A_{\Gamma}$ with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations:

@@
